Carbonate chemistry at Ny-Ålesund

### 2021-11-25 awipev-CO2.Rmd

d_all <- as_tsibble(d_hour, index = datetime) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)
```

@@

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, year, montht)
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))

# remove outliers
quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))

>>>>

d_all <- as_tsibble(d_hour, index = datetime) #d_all will be the merger
d_all <- d_all %>%
  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
      pressure_insitu_ctd <= 2,
      1,
      ifelse(
        pressure_insitu_ctd > 2 & depth <= 4,
        3,
        ifelse(
          pressure_insitu_ctd > 4 & depth <= 6,
          5,
          ifelse(
            pressure_insitu_ctd > 6 & depth <= 8,
            7,
            ifelse(pressure_insitu_ctd > 8, 10, NA)
          )
        )
      )
    ),
    depth_group_philipp = ifelse( # create new variable depth
      depth <= 2,
      1,
      ifelse(
        depth > 2 & depth <= 4,
        3,
        ifelse(
          depth > 4 & depth <= 6,
          5,
          ifelse(
            depth > 6 & depth <= 8,
            7,
            ifelse(depth > 8, 10, NA)
          )
        )
      )
    )) %>%
  dplyr::rowwise() %>% 
  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours 
    # for which there are CTD data at more than 1 depth 
  c(
    sal_insitu_ctd_1m,
    sal_insitu_ctd_3m,
    sal_insitu_ctd_5m,
    sal_insitu_ctd_7m,
    sal_insitu_ctd_9m
  )
), na.rm = TRUE)) %>% 
  ungroup()
#restore datetime, date which are mangled by the mutates above, arrange ascending
d_all <- d_all %>% 
  dplyr::mutate(datetime = d_hour$datetime, 
                date = d_hour$date,
                year = lubridate::year(d_hour$datetime), # year as a number
                monthd = lubridate::month(d_hour$datetime), # month as a number
                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
  )
rm(d_hour)
```

@@

# we look at all depths
tmp <- d_all %>% 
  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
  dplyr::group_by(depth_discrete, year, montht) %>% 
  dplyr::mutate(quant_01 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.05)),
                quant_99 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.95)),
                mean = mean(pHint_tot_sf, na.rm =TRUE),
                sd = sd(pHint_tot_sf, na.rm =TRUE)
                ) %>% 
  dplyr::filter(pHint_tot_sf < mean + sd, pHint_tot_sf > mean - sd) # remove outliers
#  dplyr::filter(pHint_tot_sf < quant_99, pHint_tot_sf > quant_01) # remove outliers
summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
